---
title: "ptg meta analysis descriptives"
author: "Qizhou Duan"
date: "2023-08-19"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(psych)
library(readxl)
```

# Load Data
Load T1 Raw for main-analysis
```{r}
ptg_effect_sizes <- read_excel("Covid T1 Raw.xlsx")
head(ptg_effect_sizes)   
```

# how many measures are we considering
```{r}
## print out the scale types
unique(ptg_effect_sizes$`scale type`)
## how many 
length(unique(ptg_effect_sizes$`scale type`)) - 2
## group by scale types and examine
ptg_effect_sizes %>% group_by(`scale type`) %>% count() 
```
NA is the additional column where I summed all the sample sizes and thus should not be included as a study; I will fix it later. 

In total we can see that we have got 13 studies with PTGI (PTG-21 is PTGI), 8 studies with PTGI-SF; 

The standard deviations I am in the process of enteringt them in for calculating effect sizes. 

# get numbers from all PTGI-measures
## overview of the ptgi studies
```{r}
ptgi_studies = ptg_effect_sizes %>% filter(`scale type` == 'PTGI' | `scale type` == 'PTG-21')
ptgi_studies
```

## descriptives for ptgi measures
```{r}
describe(as.numeric(ptgi_studies$`effect size`))
```

# get numbers from all PTGI-SF measures
```{r}
ptgisf_studies = ptg_effect_sizes %>% filter(`scale type` == 'PTGI-SF')
ptgisf_studies
```

## descriptives for ptgi-sf measures
```{r}
describe(as.numeric(ptgi_studies$`effect size`))
```
This needs a bit more work as some of the PTGI-SF studies reported the average score of each item instead of summing all the items; at the same time two studies reported percentages instead of actuall ptgi-sf values. 







